\documentclass{article}

\usepackage[english]{babel}
\usepackage{enumitem}
\usepackage[empty]{fullpage}
\usepackage[colorlinks,urlcolor=cyan]{hyperref}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{xcolor}

\pagestyle{empty}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1in}

\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-4pt}]

\newcommand{\resumeProject}[1]{\small{\textbf{#1}{:}}}
\newcommand{\resumeProjectWithDescription}[2]{\small{\textbf{#1}{: #2\vspace{-2pt}}}}
\newcommand{\resumeProjectItem}[1]{\item\small{{#1}}}

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1}&#2 \\
      \textit{\small#3}&\textit{\small#4} \\
    \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\vspace{-4pt}\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\begin{document}

%----------------HEADER----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large George Lim}&\href{mailto:lim.george@me.com}{lim.george@me.com} \\
  \href{https://www.linkedin.com/in/george-lim}{linkedin.com/in/george-lim}&\href{https://george-lim.github.io}{george-lim.github.io} \\
\end{tabular*}

%---------------EDUCATION--------------
\section{Education}
  \resumeSubHeadingListStart{}
    \resumeSubheading{University of Waterloo}{Waterloo, ON}{Bachelor of Computer Science, Honours, Co-operative Program, Philosophy Minor}{Sept 2016 \textendash{} Apr 2021}
  \resumeSubHeadingListEnd{}

%--------------EXPERIENCE--------------
\section{Experience}
  \resumeSubHeadingListStart{}
    \resumeSubheading{Duolingo}{Pittsburgh, PA}{Senior Software Engineer}{Aug 2024 \textendash{} Present}
      \resumeItemListStart{}
        \resumeProjectItem{Brainstormed, prototyped, and shipped Memory Jam challenge for music course. Discussed and implemented 40+ feedback items, triaged feedback and bugs from dogfooding sessions, integrated Rive animations.}
        \resumeProjectItem{Led efforts on Beat Blaster, the first polyphonic music challenge. Created a V1 prototype which required reimplementing song pausing, rewind, and grading behavior to support multiple simultaneous user inputs.}
        \resumeProjectItem{Rewrote client-generated daily refresh lesson nodes to work with both client and backend generated courses. Required deep understanding of various architectures, from ROCKS database to client-side course serialization and persistence.}
        \resumeProjectItem{Implemented course resurrection notification on iOS, which involved learning the existing client messaging architecture.}
        \resumeProjectItem{Built music staff line highlighting to help users visualize pitches relative to the staff.}
        \resumeProjectItem{Created staff token ear training challenge for music course. Allows users to practice identifying notes on the staff through listening to notes.}
      \resumeItemListEnd{}

    \resumeSubheading{Bunch}{Manhattan, NY}{Senior Software Engineer}{Jan 2022 \textendash{} May 2024}
      \resumeProject{Bunch Unicorn}
      \resumeItemListStart{}
        \resumeProjectItem{Implemented UI + P2P synchronization logic for watching YouTube together in a party.}
        \resumeProjectItem{Lead the clubs project, which allows up to 50 people to join a club and chat. Worked on club creation + deletion flows, club presence, club roles, club chat, push and in-app notifications, analytics.}
        \resumeProjectItem{Worked on status profile customizations (weather, emote, pose).}
        \resumeProjectItem{Added AI avatar generation through text (dictation), selfie, gallery upload, Bitmoji.}
        \resumeProjectItem{Implemented games tab and catalog, including search and all related screens to select and launch into a game from a party. Created app installation scanner and tracker on both platforms to suggest games.}
        \resumeProjectItem{Implemented space tab, including search, recent spaces, joining party by code. Includes gRPC API, repository, view model, view, caches.}
        \resumeProjectItem{Added batch DB writes to improve search performance.}
        \resumeProjectItem{Added temporary and permanent ban logic as part of toxicity model.}
        \resumeProjectItem{Created in-app review flow for iOS and Android.}
        \resumeProjectItem{Built expanded and minimized video overlay + party controls.}
        \resumeProjectItem{Built parental controls system to control various actions kids can take in Bunch.}
        \resumeProjectItem{Created a PoC to update Bunchie status and pose based on live status update from Discord and Line.}
      \resumeItemListEnd{}
      \resumeProjectWithDescription{Bunch Game SDK}{Lead the iOS SDK that provided voice and video chat integration with games, used by Miniclip.}
      \resumeItemListStart{}
        \resumeProjectItem{Designed every layer, including API, persistence, repository, view model, UI.}
        \resumeProjectItem{Added 70\% test coverage for all relevant business logic.}
        \resumeProjectItem{Added programmatic controls for video bubble, and expandable / collapsable state.}
        \resumeProjectItem{Implemented Session handover between SDK and Unicorn app.}
        \resumeProjectItem{Added automatic party restoration in boot path.}
        \resumeProjectItem{Wrote extensive sample app for testing out all SDK features.}
        \resumeProjectItem{Built presence system to notify friends when user is playing the game.}
      \resumeItemListEnd{}
      \resumeProjectWithDescription{Bunch iOS Widget}{Lead the widget extension project to view friend statuses from home screen.}
      \resumeItemListStart{}
        \resumeProjectItem{Added all networking logic (retrier, auth), custom SwiftUI components.}
      \resumeItemListEnd{}

    \resumeSubheading{Bunch}{Manhattan, NY}{Software Engineer}{Feb 2021 \textendash{} Jan 2022}
      \resumeProject{Bunch Presence SDK}
      \resumeItemListStart{}
        \resumeProjectItem{Implemented the iOS UI + KMM business logic for most of the presence matrix between the user and a friend, handling the following combinations: online / offline, alone vs in a party, public vs private party, full party.}
        \resumeProjectItem{Refactored business logic out many existing friend list views and into KMM view models, conforming to MVVM. Increased testability across iOS and Android by leveraging JUnit and Mockk for view model tests.}
        \resumeProjectItem{Introduced UserDefaults to the SDK for persisting configuration options, and Keychain for storing auth credentials.}
        \resumeProjectItem{Rewrote existing event bus architecture:}
        \resumeItemListStart{}
          \resumeProjectItem{Fixed retention cycle issues due to events having reference to queue.}
          \resumeProjectItem{Implemented event logger as event observer.}
        \resumeItemListEnd{}
        \resumeProjectItem{Set up CI/CD pipeline with BitRise, with automated notifications to Slack.}
        \resumeProjectItem{Added various in-app and push notifications like friend online, friend requested, friend added, etc.}
      \resumeItemListEnd{}
      \resumeProjectWithDescription{Bunch Palette}{Lead the project to create a CocoaPod for Atomic Design based design system.}
      \resumeItemListStart{}
        \resumeProjectItem{Allows testing components in isolation, rapidly iterating without compiling KMM.}
        \resumeProjectItem{Supports dark mode, standardizes constraint spacing, colors, fonts, etc.}
        \resumeProjectItem{Has both SwiftUI and UIKit support, with SwiftUI extensions to bridge to KMM flows.}
        \resumeProjectItem{Used to prototype party overlay with dynamic video feed layout.}
      \resumeItemListEnd{}
      \resumeProject{Bunch Unicorn}
      \resumeItemListStart{}
        \resumeProjectItem{Implemented the original onboarding flow, with support for Apple login, phone number auth, Facebook auth, and Snap login\@. Supports Firebase deferred deep link for express onboarding.}
        \resumeProjectItem{Added friends list feature, which includes ranking, search, presence session events, profile page, suggested friends, caching for search results.}
      \resumeItemListEnd{}
      \resumeProjectWithDescription{Bunch Chromecast Extension}
        {Allows friends to play games on their devices, while having the party's video streams displayed on the TV similar to Jackbox.TV.} \\
      \vspace{4pt}\resumeProjectWithDescription{Ethereum Wallet Connect}
        {Built as an internal hackathon project, allows users to connect their Ethereum wallets to Bunch so that we can read transactions into Bunch avatar clothing.}

    \resumeSubheading{McAfee, LLC (TunnelBear)}{Toronto, ON}{iOS and macOS Software Engineer; \href{https://george-lim.github.io/evaluations/evaluation-3b.pdf}{Outstanding Evaluation}}{Jan 2020 \textendash{} Apr 2020}
      \resumeItemListStart{}
        \resumeItem{Data Persistence}
          {Developed a disk persistence framework that supports different crypts (AES256-CBC), serializers, and IO managers to persist models without UserDefaults or Core Data. Makes fallback API calls with Alamofire on disk load failure.}
        \resumeItem{Analytics}
          {Wrote analytics library with AppsFlyer and Kibana integration. Provides bulk processing analytics events, event caching, and client-server event upload synchronization.}
        \resumeItem{State Monitoring}
          {Replaced MirrorDiffKit with a custom logic that dynamically identifies state differences between objects. Allows logging Redux state changes. Bypasses Swift's static type nature using code generation via Sourcery framework.}
        \resumeItem{Test-Driven Development}
          {Wrote extensive unit tests for VPN connection queue, Keychain accessor, and Store + Actions (Redux) systems. Improved queue recovery logic and fixed logout issues caused by API Keychain token not deleting.}
      \resumeItemListEnd{}

    \resumeSubheading{McAfee, LLC (TunnelBear)}{Toronto, ON}{iOS Software Engineer; \href{https://george-lim.github.io/evaluations/evaluation-3a.pdf}{Outstanding Evaluation}}{May 2019 \textendash{} Aug 2019}
      \resumeItemListStart{}
        \resumeItem{Migrator}
          {Rewrote app migrator to properly handle account and connection state transition for existing v2.x users.}
        \resumeItem{Gateway}
          {BlueBear is a fallback AWS gateway that enables VPN clients to connect to TunnelBear servers when the primary gateway is blocked by ISPs. Integrated BlueBear v2 into iOS client, with fallback connection performance optimizations.}
        \resumeItem{Logging}
          {Rewrote logging library in Swift, decoupling objective-zip dependency. Uses CocoaLumberjackLogger, with support for dependency injection and sending logs using multi-part form data requests.}
        \resumeItem{Cryptography}
          {Built \href{https://github.com/george-lim/envelope}{Envelope}, an open-source hybrid cryptosystem that encrypts files using different symmetric and public-key ciphers. Supports AES256-CBC and RSA-2048. Used to secure logs in fallback log upload system.}
        \resumeItem{App Ratings}
          {Implemented custom app rating framework to replace deprecated ``iRate'' dependency.}
        \resumeItem{Connection Improvements}
          {Removed redundancies in reachability logic which decreased time to resolve connection errors by 50\%. Fixed a critical bug which spammed analytics endpoint on every app state change.}
      \resumeItemListEnd{}

    \resumeSubheading{Bunch}{Manhattan, NY}{Software Engineer; \href{https://george-lim.github.io/evaluations/evaluation-2b.pdf}{Outstanding Evaluation}}{Sept 2018 \textendash{} Dec 2018}
      \resumeItemListStart{}
        \resumeItem{Camera SDK}
          {Developed an improved camera layout system in React Native that allows developers to easily add camera position animations and transitions for each lobby participant. Used to animate cameras as members join or leave a lobby.}
        \resumeItem{CallKit}
          {Integrated CallKit as a proof of concept way to join a game lobby with friends from outside the app.}
        \resumeItem{UI Components}
          {Created DynamicPopup and DynamicModal, two custom React Native ScrollView components with multiple rest states and the ability to support sticky headers and footers. Used in every notification UI popup.}
      \resumeItemListEnd{}

    \resumeSubheading{TunnelBear}{Toronto, ON}{iOS Software Engineer; \href{https://george-lim.github.io/evaluations/evaluation-2a.pdf}{Outstanding Evaluation}}{Jan 2018 \textendash{} Apr 2018}
      \resumeItemListStart{}
        \resumeItem{TBMapKit}
          {Developed TBMapKit, a CocoaPods MapKit framework for iOS and macOS that increases map render speeds by selectively caching and rendering map regions. Refactored TunnelBear's tunnel animation framework into TBMapKit.}
        \resumeItem{BlockBear}
          {Optimized time to import and process website block list. Fixed font blocking feature, migrated app to Swift 4.}
        \resumeItem{Rate Limiting (Captcha)}
          {Discovered a solution to WKWebView's bug of blocking cookies on first connection, which fixed CloudFlare cookie verification. Unblocked and shipped the rate-limiting feature to iOS.}
        \resumeItem{Refactor}
          {Refactored TBMainViewController consisting of 3000+ lines of Objective-C code into four Swift controllers.}
        \resumeItem{Payment System}
          {Integrated Apple's free trial subscription model, involving onboarding UI and payment system upgrades.}
      \resumeItemListEnd{}

    \resumeSubheading{Z1}{Toronto, ON}{Software Engineer; \href{https://george-lim.github.io/evaluations/evaluation-1b.pdf}{Outstanding Evaluation}}{Jan 2018 \textendash{} Apr 2018}
      \resumeItemListStart{}
        \resumeItem{Signal Processing}
          {Optimized RxSwift signal funnel when parsing calendar event data from Realm, reducing amount of debounced asynchronous signals by over 5x.}
        \resumeItem{Zoom}
          {Integrated Zoom's MobileRTC stack, allowing users to make Zoom conference calls directly from a calendar event.}
        \resumeItem{Calendar Widget}
          {Wrote a shared library for today extension widget and rich notifications, using Stevia and Bonmot frameworks to create dynamic UI layouts for each calendar event type.}
      \resumeItemListEnd{}
  \resumeSubHeadingListEnd{}

%-------------PUBLICATIONS-------------
\section{Publications}
  \resumeSubHeadingListStart{}
    \resumeSubItem{\href{https://www.kumo.tk}{Kumo}}
      {A progressive web app written in Rust + WebAssembly that lets users watch anime and read manga online with friends.}
    \resumeSubItem{\href{https://t.me/WealthsimpleBot}{Wealthsimple Bot}}
      {A Telegram bot written in Rust + WebAssembly that manages Wealthsimple Trade accounts and orders.}
    \resumeSubItem{\href{https://crates.io/crates/ordered-pool-allocator}{Ordered Pool Allocator}}
      {A fast and compact pool allocator with block sorting support.}
    \resumeSubItem{\href{https://github.com/george-lim/aer-world}{AER World}}
      {A game state container designed to model games where entities can react to actions by spawning more actions.}
    \resumeSubItem{\href{https://cocoapods.org/pods/envelope}{Envelope}}
      {OpenSSL-compatible file encryption in Swift.}
    \resumeSubItem{\href{https://github.com/george-lim/nephele}{Nephele}}
      {An AWS serverless application written in Python that hosts George's cloud-compatible side projects.}
    \resumeSubItem{\href{https://appadvice.com/app/spikeful/1265332106}{Spikeful}}
      {An accelerometer-based iOS game made using SpriteKit designed to compete against Ketchapp.}
    \resumeSubItem{\href{https://play.google.com/store/apps/details?id=com.bruno.android}{Bruno}}
      {An Android music discovery fitness app that turns your playlist into a fitness partner that competes against you.}
    \resumeSubItem{\href{https://appadvice.com/app/dialer/1266511331}{Dialer}}
      {A super fast Zoom conferencing tool on iOS.}
    \resumeSubItem{\href{https://appadvice.com/app/traffic-pal/1265505042}{Traffic Pal}}
      {A traffic simulation tool developed for CARS Education on iOS.}
  \resumeSubHeadingListEnd{}

\end{document}
